Model LF

### 2022-11-26 max_dp endogen stød.Rmd
Commit

@@

```{r}
plot(((yk_ds_s1_up-yk_ds_sb_up)/yk_ds_sb_up)*100, col= "red", xlab= "Year", ylab= "% Change in GDP", main= "Sensitivity of GDP");
lines(((yk_ds_s1_low-yk_ds_sb_low) /yk_ds_sb_low)*100, col="black");
lines(((yk_ds_01 -yk_ds_00) /yk_ds_00)*100, col="blue");
legend("top", legend=c("Estimate 0.99",
                       "Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

@@

```{r}
plot((unemp_s1_up-unemp_sb_up)*1000, col= "red", xlab= "Year", ylab= "Change in Unemployment (people)", main= "Sensitivity of Unemployment");
lines((unemp_s1_low-unemp_sb_low)*1000, col="black");
lines((unemp_01-unemp_00)*1000, col="blue");
legend("left", legend=c("Estimate 0.99",
                       "Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

@@

```{r}
plot(((wage_ds_t_s2_up-wage_ds_t_sbs2_up)/wage_ds_t_sbs2_up)*100, col= "red", ylab= "% change in Target Wage" ,  main= "Targeted Wage");
lines(((wage_ds_t_s2_low- wage_ds_t_sbs2_low)/wage_ds_t_sbs2_low)*100, col="black");
lines(((wage_ds_t_02-wage_ds_t_bs2)/wage_ds_t_bs2)*100, col="blue");
legend("top", legend=c("Wage-gap limit 44%",
                       "Wage-gap limit 40%",
                       "Wage-gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

@@

```{r}
plot(((yk_ds_s3_low-yk_ds_sbs3_low )/yk_ds_sbs3_low)*100, col= "red", ylab= "% Change in GDP", main= "Sensitivity of GDP");
lines(((yk_ds_03 - yk_ds_bs3)/yk_ds_bs3)*100, col="black");
legend("top", legend=c("Estimate set to 0.5",
                       "Estimate set to 1"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

>>>>

```{r, fig.height=7, fig.width=10}

par(mfrow=c(1,2))
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0015, 0.0015));
lines(((yk_ds_07b - yk_ds_bs7b) / yk_ds_bs7b), col= "red");
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("left", legend=c("All channels", "All channels but productivity","Insurance rate channel","Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "red","yellow", "black","orange", "green"));
grid()

plot(((unemp_05 - unemp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Sensitivity of Unemployment", ylim= c(0,25000));
lines(((unemp_07b - unemp_bs7b)*1000), col= "red");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "green");
legend("left", legend=c("All channels", "All channels but productivity","Productivity channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "red", "green"));
grid()

```
```{r}
plot(((unemp_05 - unemp_bs56)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Sensitivity of Unemployment", ylim= c(0,25000));
lines(((unemp_07b - unemp_bs7b)*1000), col= "red");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "green");
legend("left", legend=c("All channels", "All channels but productivity","Productivity channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "red", "green"));
grid()
```

@@

plot(((yk_ds_s1_up-yk_ds_sb_up)/yk_ds_sb_up)*100, col= "red", xlab= "Year", ylab= "% Change in GDP", main= "Sensitivity of GDP");
lines(((yk_ds_s1_low-yk_ds_sb_low) /yk_ds_sb_low)*100, col="black");
lines(((yk_ds_01 -yk_ds_00) /yk_ds_00)*100, col="blue");
legend("top", legend=c("Estimate 0.99",
                       "Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

plot((unemp_s1_up-unemp_sb_up)*1000, col= "red", xlab= "Year", ylab= "Change in Unemployment (people)", main= "Sensitivity of Unemployment");
lines((unemp_s1_low-unemp_sb_low)*1000, col="black");
lines((unemp_01-unemp_00)*1000, col="blue");
legend("left", legend=c("Estimate 0.99",
                       "Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

@@

@@

par(mfrow=c(2,2))

plot(((wage_ds_t_s2_up-wage_ds_t_sbs2_up)/wage_ds_t_sbs2_up)*100, col= "red", ylab= "% change in Target Wage" ,  main= "Targeted Wage");
lines(((wage_ds_t_s2_low- wage_ds_t_sbs2_low)/wage_ds_t_sbs2_low)*100, col="black");
lines(((wage_ds_t_02-wage_ds_t_bs2)/wage_ds_t_bs2)*100, col="blue");
legend("top", legend=c("Wage-gap limit 44%",
                       "Wage-gap limit 40%",
                       "Wage-gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

plot(((wage_ds_s2_up-wage_ds_sbs2_up)/wage_ds_sbs2_up)*100, col= "red", ylab="% change in Wages", main= "Wage");
lines(((wage_ds_s2_low-wage_ds_sbs2_low)/wage_ds_sbs2_low)*100, col="black");
lines(((wage_ds_02-wage_ds_bs2)/wage_ds_bs2)*100, col="blue");
legend("top", legend=c("Wage-gap limit 44%",
                       "Wage-gap limit 40%",
                       "Wage-gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

plot((unemp_s2_up - unemp_sbs2_up)*1000, col= "red", ylab= "Change in Unemployment (people)", main= "Sensitivity of Unemployment");
lines((unemp_s2_low - unemp_sbs2_low)*1000, col="black");
lines((unemp_02 - unemp_bs2)*1000, col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

plot(((yk_ds_s2_up-yk_ds_sbs2_up) / yk_ds_sbs2_up)*100, col= "red", ylab= "% Change inm GDP", main= "Sensitivity of GDP");
lines(((yk_ds_s2_low -yk_ds_sbs2_low)/ yk_ds_sbs2_low)*100, col="black");
lines(((yk_ds_02 -yk_ds_bs2)/ yk_ds_bs2)*100, col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

@@

plot(((yk_ds_s3_low-yk_ds_sbs3_low )/yk_ds_sbs3_low)*100, col= "red", ylab= "% Change in GDP", main= "Sensitivity of GDP");
lines(((yk_ds_03 - yk_ds_bs3)/yk_ds_bs3)*100, col="black");
legend("top", legend=c("Estimate set to 0.5",
                       "Estimate set to 1"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()

plot((unemp_s3_low-unemp_sbs3_low)*1000, col= "red", ylim= c(0,25000), ylab= "% Change in Unemployment", main= "Sensitivity of unemployment");
lines((unemp_03-unemp_bs3)*1000, col="black");
legend("top", legend=c("Estimate set to 0.5",
                       "Estimate set to 1"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```
